Measuring individual differences in the understanding of gaze cues across the lifespan

### 2022-01-05 paper/manuscript.Rmd
start writing prolific supplement

>>>>

# Supplements

## Adult sample

### Recruitment
We recruited participants using the online participant recruitment service 
*Prolific* from the University of Oxford. 
*Prolific*'s subject pool consists of a mostly European and US-american sample 
although subjects from all over the world are included.

The recruitment platform realises ethical payment of participants, 
which requires researchers to pay participants a fixed minimum wage  
of £5.00 (around US$6.50 or €6.00) per hour.
We decided to pay all participants the same fixed fee which was in relation 
to the estimated average time taken to complete the task.

*Prolific* distributed our study link to potential participants, 
while the hosting of the online study was done by local servers in the
Max Planck Institute for Evolutionary Anthropology, Leipzig. 
Therefore, study data was saved only on our internal servers, 
while *Prolific* provided demographic information of the participants.

Participants' *Prolific* ID was forwarded to our study website using URL parameters.
This way, we could match participant demographic data to our study data. 
The same technique was used to confirm study completion: 
we redirected participants from our study website back to the *Prolific* website 
using URL parameters.

We used *Prolific*'s inbuilt prescreening filter to include 
only participants who were fluent in English
and could therefore properly understand our written and oral study instructions.

### Study 1 - Validation hedge version
We recruited participants online by advertising the study on *Prolific*.

50 adults participated in the study. 
One additional subject returned their submission,
i.e., decided to leave the study early or withdrew their submission after study completion.
Data collection took place in May 2021.

Participants were compensated with £1.25 for completing the study. 
We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
In average, participants took 05:56min to complete the study.

Participants were required to complete the study on a tablet or desktop. 
Participation on mobile devices was disabled 
since the display would be too small and would harm click precision.
It was indicated that the study required audio sound.

We stored *Prolific*'s internal demographic information, 
while not asking for additional personal information.

After clicking the study title, participants were directed to our online study website.
...

### Study 2 - Validation box version
As in study 1, we recruited participants on *Prolific*, and employed the same methodology. 
However, this time participants were presented with the box version of the task.
We showed eight boxes in which the target could land.

50 adults participated in the study. 
One additional subject returned their submission,
i.e., decided to leave the study early or withdrew their submission after study completion.
Data collection took place in June 2021.

Participants were compensated with £1.00 for completing the study. 
We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
In average, participants took 04:43min to complete the study.

### Study 3 - Reliability hedge version
In addition to the beforementioned prescreening settings, we used a whitelist.

whitelist screener: 
"When the researcher uses a whitelist, 
only participants with IDs entered into the whitelist are invited to participate in a study. 
This allows gathering information from the same subjects at different points in time."

### Study 4 - Reliability box version
As in study 3, we recruited participants on *Prolific*, and employed the same methodology. 
However, this time participants were presented with the box version of the task.
As in study 2, we employed eight boxes in which the target could land.

### 2022-01-05 paper/manuscript.tex
start writing prolific supplement

>>>>

\hypertarget{supplements}{%
\section{Supplements}\label{supplements}}

\hypertarget{adult-sample}{%
\subsection{Adult sample}\label{adult-sample}}

\hypertarget{recruitment}{%
\subsubsection{Recruitment}\label{recruitment}}

We recruited participants using the online participant recruitment service
\emph{Prolific} from the University of Oxford.
\emph{Prolific}'s subject pool consists of a mostly European and US-american sample
although subjects from all over the world are included.

The recruitment platform realises ethical payment of participants,
which requires researchers to pay participants a fixed minimum wage\\
of £5.00 (around US\$6.50 or €6.00) per hour.
We decided to pay all participants the same fixed fee which was in relation
to the estimated average time taken to complete the task.

\emph{Prolific} distributed our study link to potential participants,
while the hosting of the online study was done by local servers in the
Max Planck Institute for Evolutionary Anthropology, Leipzig.
Therefore, study data was saved only on our internal servers,
while \emph{Prolific} provided demographic information of the participants.

Participants' \emph{Prolific} ID was forwarded to our study website using URL parameters.
This way, we could match participant demographic data to our study data.
The same technique was used to confirm study completion:
we redirected participants from our study website back to the \emph{Prolific} website
using URL parameters.

We used \emph{Prolific}'s inbuilt prescreening filter to include
only participants who were fluent in English
and could therefore properly understand our written and oral study instructions.

\hypertarget{study-1---validation-hedge-version}{%
\subsubsection{Study 1 - Validation hedge version}\label{study-1---validation-hedge-version}}

We recruited participants online by advertising the study on \emph{Prolific}.

50 adults participated in the study.
One additional subject returned their submission,
i.e., decided to leave the study early or withdrew their submission after study completion.
Data collection took place in May 2021.

Participants were compensated with £1.25 for completing the study.
We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
In average, participants took 05:56min to complete the study.

Participants were required to complete the study on a tablet or desktop.
Participation on mobile devices was disabled
since the display would be too small and would harm click precision.
It was indicated that the study required audio sound.

We stored \emph{Prolific}'s internal demographic information,
while not asking for additional personal information.

After clicking the study title, participants were directed to our online study website.
\ldots{}

\hypertarget{study-2---validation-box-version}{%
\subsubsection{Study 2 - Validation box version}\label{study-2---validation-box-version}}

As in study 1, we recruited participants on \emph{Prolific}, and employed the same methodology.
However, this time participants were presented with the box version of the task.
We showed eight boxes in which the target could land.

50 adults participated in the study.
One additional subject returned their submission,
i.e., decided to leave the study early or withdrew their submission after study completion.
Data collection took place in June 2021.

Participants were compensated with £1.00 for completing the study.
We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
In average, participants took 04:43min to complete the study.

\hypertarget{study-3---reliability-hedge-version}{%
\subsubsection{Study 3 - Reliability hedge version}\label{study-3---reliability-hedge-version}}

In addition to the beforementioned prescreening settings, we used a whitelist.

whitelist screener:
``When the researcher uses a whitelist,
only participants with IDs entered into the whitelist are invited to participate in a study.
This allows gathering information from the same subjects at different points in time.''

\hypertarget{study-4---reliability-box-version}{%
\subsubsection{Study 4 - Reliability box version}\label{study-4---reliability-box-version}}

As in study 3, we recruited participants on \emph{Prolific}, and employed the same methodology.
However, this time participants were presented with the box version of the task.
As in study 2, we employed eight boxes in which the target could land.
